### 2018-06-19 paper/4-build.tex
Expand the table

@@

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||c|c|c}
\hline
Property           & Topological\hspace{2mm}\S\ref{sec-topological} & Restarting\hspace{2mm}\S\ref{sec-restarting} & Suspending\hspace{2mm}\S\ref{sec-suspending}    \\\hline
\hline
Dirty bit\hfill\S\ref{sec-dirty-bit}                    & \Make    & \Excel                   & Approximate \Shake*  \\\hline
Verifying trace\hfill\S\ref{sec-verifying-traces}       & \Ninja   & Traced \Excel*            & \Shake                      \\\hline
Constructive trace\hspace{2mm}\hfill\S\ref{sec-constructive-traces} & \Bazel   & Cloud \Excel*             & Cloud \Shake*                \\\hline
\end{tabular}
\vspace{2mm}
\caption{Build systems \`a la carte. Systems marked * are hypothetical systems that do not currently exist.\label{tab-build-systems}}
\vspace{-2mm}
\end{table}

>>>>

\subsubsection{Deterministic constructive traces}\label{sec-deterministic-constructive-traces}

\textbf{TODO}

@@

\begin{table}[h]
\smaller
\centering
\begin{tabular}{l||c|c|c}
\hline
Property           & Topological\hspace{2mm}\S\ref{sec-topological} & Restarting\hspace{2mm}\S\ref{sec-restarting} & Suspending\hspace{2mm}\S\ref{sec-suspending}    \\\hline
\hline
Dirty bit\hfill\S\ref{sec-dirty-bit}                                                             & \Make       & \Excel & -              \\\hline
Verifying traces\hfill\S\ref{sec-verifying-traces}                                               & \Ninja      & -      & \Shake         \\\hline
Constructive traces\hspace{2mm}\hfill\S\ref{sec-constructive-traces}                             & \CloudBuild & \Bazel & \Cloud \Shake  \\\hline
Deterministic constructive traces\hspace{2mm}\hfill\S\ref{sec-deterministic-constructive-traces} & \Buck       & -      & \Nix           \\\hline
\end{tabular}
\vspace{2mm}
\caption{Build systems \`a la carte.\label{tab-build-systems}}
\vspace{-2mm}
\end{table}

### 2018-06-19 paper/5-implementations.tex
Expand the table

Fig.~\ref{fig-buck-nix-implementation} shows our models of \Buck and \Nix build
systems that use the \hs{dctRebuilder} -- a rebuilder based on deterministic
constructive traces. As one can see, \hs{dctRebuilder} is almost identical to
\hs{ctRebuilder}, but it ignores the current \hs{value}, since the
\hs{constructDCT} query only needs to examine the transitive inputs of the given
\hs{key}. \Buck uses the \hs{topological} scheduler and is therefore an
applicative build system, whereas \Nix uses the \hs{suspending} scheduler and is
monadic.

>>>>

Fig.~\ref{fig-buck-nix-implementation} shows our models of \Buck and \Nix build
systems that use the \hs{dctRebuilder} -- a rebuilder based on deterministic
constructive traces (\S\ref{sec-deterministic-constructive-traces}). As one can
see, \hs{dctRebuilder} is almost identical to \hs{ctRebuilder}, but it ignores
the current \hs{value}, since the \hs{constructDCT} query only needs to examine
the transitive inputs of the given \hs{key}. \Buck uses the \hs{topological}
scheduler and is therefore an applicative build system, whereas \Nix uses the
\hs{suspending} scheduler and is monadic.
